Product plots

### 2011-06-23 prodplots-infovis.tex
added model names to figure 6
overlooked a centering
width of figure 4
additional labels on the plots
additional legends comments

\begin{figure}[htbp]
  \centering
    \includegraphics[width=0.9 \linewidth]{part-fluct}
    \includegraphics[width=0.9 \linewidth]{part-fluct-cond}
  \caption{(Top) A fluctuation diagram showing distribution of age (in decades) and marital status. (Bottom) Equal bin-size plot showing health status and survey year. Thee three empty columns show that health status was not recorded for three years.}
  \label{fig:fluct}
\end{figure}

@@

\begin{figure}[ht]
  \begin{tabular}{rrr}
  \toprule
  & male & female \\ 
  \midrule
  not too happy & 0.05 & 0.07 \\ 
  pretty happy & 0.25 & 0.31 \\ 
  very happy & 0.14 & 0.18 \\ 
  \bottomrule
  \end{tabular}
  \\[1em]

  \begin{tabular}{rrr}
  \toprule
  & male & female \\
  \midrule
  not too happy & 0.43 & 0.57 \\
  pretty happy & 0.45 & 0.55 \\ 
  very happy & 0.43 & 0.57 \\
  \bottomrule
  \end{tabular}\hspace{1em}%
  \begin{tabular}{rrr}
  \toprule
  & male & female \\ 
  \midrule
  not too happy & 0.12 & 0.12 \\ 
  pretty happy & 0.57 & 0.55 \\ 
  very happy & 0.31 & 0.32 \\
  \bottomrule
  \end{tabular}
  \\[1em]

  \begin{tabular}{rrrr}
  \toprule
  & male & female & \\ 
  \midrule
  not too happy & & & 0.12 \\ 
  pretty happy & & & 0.56 \\ 
  very happy & & & 0.30 \\
  & 0.44 & 0.56 \\ 
  \bottomrule
  \end{tabular}

@@

\begin{figure}[htbp]
  \centering
    \includegraphics[width=0.33\linewidth]{part-comb-1}%
    \includegraphics[width=0.33\linewidth]{part-comb-2}%
    \includegraphics[width=0.33\linewidth]{part-comb-3}
  \caption{Conditional on marital status, are men or women happier?  This figure shows the construction of $f(happy, sex, marital)$ with (from left to right) a vspine by marital status, a vspine by marital status and sex, and a hspine by marital status, sex and happiness.  For all levels of marital status, men are slightly less happy.}
  \label{fig:recursive}
\end{figure}

@@

\begin{figure}[htbp]
  \centering
    \includegraphics[width=0.5\linewidth]{part-marital-1}%
    \includegraphics[width=0.5\linewidth]{part-marital-2}
  \caption{(Left) The joint distribution of marital status and age, $f(marital, age)$, (in decades) partitioned by a vspine and hspine.  (Right) The joint distribution of age and marital status, $f(age, marital)$, partitioned by a vspine and hbar.}
  \label{fig:marital}
\end{figure}

@@

\begin{figure*}[htbp]
  \centering
    \includegraphics[width=0.33\linewidth]{part-fluctuation}%
    \includegraphics[width=0.33\linewidth]{part-equal-area}%
    \includegraphics[width=0.33\linewidth]{part-equal-area-2}
  \caption{(Left) $f(happy, health, finrela) = f(happy | health, finrela) \times f(health, finrela)  $, partitioned with a vspine and fluct.  Health is on the $x$-axis, financial status on the $y$-axis. (Middle) $f(happy | health, finrela)$. We can no longer see the joint distribution of health and financial status, but it is much easier to see the conditional distribution of happiness. Healthier and richer people are happier: maybe money does buy happiness? (Right) $f(happy | health, finrela)$ partitioned with a fluct and {\bf h}spine. (\key{not-too-happy} Not too happy, \key{pretty-happy} pretty happy, \key{very-happy} very happy)}
  \label{fig:part-cond}
\end{figure*}

>>>>

\begin{figure}[htbp]
  \centering
  $f(age, marital)$
    \includegraphics[width=0.9 \linewidth]{part-fluct}
  $f(1 | age, marital)$
    \includegraphics[width=0.9 \linewidth]{part-fluct-cond}
  \caption{(Top) A fluctuation diagram showing distribution of age (in decades) and marital status. (Bottom) Equal bin-size plot showing health status and survey year. Thee three empty columns show that health status was not recorded for three years.}
  \label{fig:fluct}
\end{figure}

@@

\begin{figure}[ht]
  \begin{tabular*}{0.5\linewidth}{rrr}
\multicolumn{3}{l}{$f(happiness, sex)$}\\
  \toprule
  & male & female \\ 
  \midrule
  not too happy & 0.05 & 0.07 \\ 
  pretty happy & 0.25 & 0.31 \\ 
  very happy & 0.14 & 0.18 \\ 
  \bottomrule
  \end{tabular*}
  \\[1em]

  \begin{tabular*}{0.48\linewidth}{rrr}
\multicolumn{3}{l}{$f(happiness| sex)$}\\
  \toprule
  & male & female \\
  \midrule
  not too happy & 0.43 & 0.57 \\
  pretty happy & 0.45 & 0.55 \\ 
  very happy & 0.43 & 0.57 \\
  \bottomrule
  \end{tabular*}
%
\hspace{1em}
  \begin{tabular*}{0.48\linewidth}{rrr}
\multicolumn{3}{l}{ $f(sex|happiness)$}\\
  \toprule
  & male & female \\ 
  \midrule
  not too happy & 0.12 & 0.12 \\ 
  pretty happy & 0.57 & 0.55 \\ 
  very happy & 0.31 & 0.32 \\
  \bottomrule
  \end{tabular*}
  \\[1em]

  \begin{tabular}{rrrr}
\multicolumn{3}{l}{$f(happiness), f(sex)$}\\
  \toprule
  & male & female & \\ 
  \midrule
  not too happy & & & 0.12 \\ 
  pretty happy & & & 0.56 \\ 
  very happy & & & 0.30 \\
  & 0.44 & 0.56 \\ 
  \bottomrule
  \end{tabular}

@@

\begin{figure}[htbp]
\begin{minipage}[b]{0.3\linewidth}
  	$f(marital)$
      \includegraphics[width=\linewidth]{part-comb-1}%
\end{minipage} 
\begin{minipage}[b]{0.3\linewidth}
$f(marital, sex)$ 
       \includegraphics[width=\linewidth]{part-comb-2}
\end{minipage} 
\begin{minipage}[b]{0.3\linewidth}
$f(happy, sex, marital) =$
$f(happy|marital, sex) \cdot $
$f(marital, sex)$
      \includegraphics[width=\linewidth]{part-comb-3}
\end{minipage}
  \caption{Conditional on marital status, are men or women happier?  This figure shows the construction of $f(happy, sex, marital)$ with (from left to right) a vspine by marital status, a vspine by marital status and sex, and a hspine by marital status, sex and happiness.  For all levels of marital status, men are slightly less happy.}
  \label{fig:recursive}
\end{figure}

@@

\begin{figure}[htbp]
  \centering
$f(marital, age) =$\\
\begin{minipage}[t]{0.49\linewidth}
\centering 
$f(marital|age)f(age)$ 
    \includegraphics[width=\linewidth]{part-marital-1}%
 \end{minipage}
\begin{minipage}[t]{0.49\linewidth}
\centering
 $f(age|marital)f(marital)$
    \includegraphics[width=\linewidth]{part-marital-2}
 \end{minipage}
  \caption{(Left) The joint distribution of marital status and age, $f(marital, age)$ as $f(marital|age) \cdot f(age)$, (in decades) partitioned by a vspine and hspine.  (Right) The joint distribution of age and marital status, $f(age, marital)$, partitioned by a vspine and hbar.}
  \label{fig:marital}
\end{figure}

@@

\begin{figure*}[htbp]
  \centering
\begin{minipage}[b]{0.32\linewidth}
\centering
$f(happy, health, finrela) =$
$f(happy | health, finrela) \times f(health, finrela)  $
     \includegraphics[width=\linewidth]{part-fluctuation}
 \end{minipage}
%
\begin{minipage}[b]{0.32\linewidth}
\centering
$f(happy | health, finrela)$
    \includegraphics[width=\linewidth]{part-equal-area}
 \end{minipage}
%
\begin{minipage}[b]{0.32\linewidth}
\centering
$f(happy | finrela, health)$
    \includegraphics[width=\linewidth]{part-equal-area-2}
 \end{minipage}
%
    %

  \caption{(Left) $f(happy, health, finrela) = f(happy | health, finrela) \times f(health, finrela)  $, partitioned with a vspine and fluct.  Health is on the $x$-axis, financial status on the $y$-axis. (Middle) $f(happy | health, finrela)$. We can no longer see the joint distribution of health and financial status, but it is much easier to see the conditional distribution of happiness. Healthier and richer people are happier: maybe money does buy happiness? (Right) $f(happy | health, finrela)$ partitioned with a fluct and {\bf h}spine, emphasizing the relationship of happiness with finances, whereas the middle plot emphasizes the relationship with health. (\key{not-too-happy} Not too happy, \key{pretty-happy} pretty happy, \key{very-happy} very happy)}
  \label{fig:part-cond}
\end{figure*}
